HEP Software Foundation Community White Paper Working Group -- Detector Simulation

### 2018-02-21 CWP/papers/HSF-CWP-2017-07_detsim/latex/DetectorSimulation.tex
changed one sentence to read better

Much of the text above concentrates on physics processes relevant to the
LHC experiments. Much of this overlaps the needs of muon and neutrino
experiments as well as dark matter and rare-decay experiments, which
have typically used Geant4 physics lists tuned based on LHC
requirements. However, as the precision needs of these experiments
increase, they increasingly need simulations responding to their
particular needs, which vary significantly with experiment but broadly
speaking involve precise simulations of hadrons and electromagnetic
particles from a few GeV to a few MeV. Precise neutron simulation is
particularly critical for accelerator-based neutrino experiments that
must reconstruct neutrino energy from final state particles. Also a
radioactive decay model for modelling the decay chain of isotopes is
essential for background studies.

>>>>

Much of the text above concentrates on physics processes relevant to the
LHC experiments. Much of this overlaps the needs of muon and neutrino
experiments as well as dark matter and rare-decay experiments, which
have typically used Geant4 physics lists tuned based on LHC
requirements. However, as the physics programs of these experiments evolve,
they require simulation of increasing accuracy, which depends significantly
on the experiment but in all cases involves accurate modeling of hadrons and
electromagnetically interacting particles from a few MeV to a few GeV.
Precise neutron simulation is
particularly critical for accelerator-based neutrino experiments that
must reconstruct neutrino energy from final state particles. Also a
radioactive decay model for modelling the decay chain of isotopes is
essential for background studies.
